$\pi$ with leftovers: \\ a mechanisation in Agda

### 2021-01-20 paper/paper.tex
Shorten contrib 2

  \item \textbf{Shared, graded and linear unified \picalc{}}.
  We {generalise resource counting to a set of usage algebras that can be mixed within the same type system}.
    We do not instantiate our type system to only work with linear resources, instead we present an algebra-agnostic type system, and admit a mix of user-defined \emph{resource aware} algebras (\autoref{multiplicities}).
    Any \emph{partial commutative monoid} that is \emph{decidable}, \emph{deterministic}, \emph{cancellative} and has a \emph{minimal element} is a valid such algebra.
    Multiple algebras can be mixed in the type system --- usage contexts keep information about what algebra to for each type (\autoref{contexts}).
    In particular, this allows for type systems combining linear (use exactly once), graded (exact number of $n$ times) and shared (free to reuse and discard) types under the same framework.
    Thanks to leftovers, our type system satisfies \emph{weakening} and \emph{strengthening} for the whole framework. In particular, these are stated for the first time for the linear \picalc{}.

>>>>

  \item \textbf{Shared, graded and linear unified \picalc{}}.
  We {generalise resource counting to a set of usage algebras that can be mixed within the same type system}.
    We do not instantiate our type system to only work with linear resources, instead we present an algebra-agnostic type system, and admit a mix of user-defined \emph{resource aware} algebras (\autoref{multiplicities}).
    Any \emph{partial commutative monoid} that is \emph{decidable}, \emph{deterministic}, \emph{cancellative} and has a \emph{minimal element} is a valid such algebra.
    Multiple algebras can be mixed in the type system --- usage contexts keep information about what algebra to for each type (\autoref{contexts}).
    In particular, this allows for type systems combining linear (use exactly once), graded (exact number of $n$ times) and shared (free to reuse and discard) types under the same framework.
    Thanks to leftover typing, we can now define \emph{weakening} and \emph{strengthening} for the whole framework, not just the shared fragment.
